---
title: "Rarefaction curves for MiFish amplicon"
author: "Enora Geslain"
date: "`r Sys.Date()`"
output:
  html_document:
    toc: true
    number_sections: true
    code_folding: hide
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(iNEXT)
library(ggplot2)
library(phyloseq)
library(metagMisc)
library(dplyr)
library(egor)
library(ggpubr)
library(gtools)
library(mrdwabmisc)
setwd("D:/Boulot-Leuven/UNESCO_eDNA/1rst_batch/rarefaction_curves")
```


# Plot rarefaction curves of Mifish amplicon for Argentina sample

```{r Argentina}
Arg <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Argentina_MiFish_2.rds")
Arg <- tax_glom(Arg, taxrank = rank_names(Arg)[15])
Arg
iNEXT_table <- otu_table(Arg) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Arg <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#4e693a","#88b564","#4e693a","#4e693a","#4e693a","#9bcf72",
             "#749b55","#9bcf72","#749b55","#749b55","#749b55","#9bcf72",
             "#ade880","gray34","#88b564","#ade880","#88b564","#88b564",
             "#9bcf72","#ade880","#ade880","gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Arg, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Arg, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Arg, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2)

```


# Plot rarefaction curves of Mifish amplicon for Bangladesh sample

```{r Bangladesh}
Ban <- readRDS("phyloseq_Bangladesh_MiFish.rds")
Ban2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Bangladesh_MiFish_2.rds")
OTU_Ban2 <- as(otu_table(Ban2), "matrix")
OTU_Ban <- as(otu_table(Ban), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Ban2), as.data.frame(OTU_Ban))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Ban2 <- as(tax_table(Ban2), "matrix")
TAXA_Ban <- as(tax_table(Ban), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Ban2), as.data.frame(TAXA_Ban))
TAXA_all <- tax_table(TAXA_all)
Ban_all <- phyloseq(OTU_all, TAXA_all)
Ban_all <- tax_glom(Ban_all, taxrank = rank_names(Ban_all)[15])
Ban_all
iNEXT_table <- otu_table(Ban_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Ban <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#407d55","#53a36f","#67c989","#67c989","#2d573c","#407d55",
             "#53a36f","#53a36f","#67c989","#2d573c","#2d573c","#53a36f",
             "#7af0a3","#7af0a3","#407d55","#2d573c","#7af0a3","#7af0a3",
             "#67c989","#193021","#407d55","grey34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Ban, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Ban, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Ban, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Belize sample

```{r Belize}
Bel <- readRDS("phyloseq_Belize_MiFish.rds")
Bel2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Belize_MiFish_2.rds")
OTU_Bel2 <- as(otu_table(Bel2), "matrix")
OTU_Bel <- as(otu_table(Bel), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Bel2), as.data.frame(OTU_Bel))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Bel2 <- as(tax_table(Bel2), "matrix")
TAXA_Bel <- as(tax_table(Bel), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Bel2), as.data.frame(TAXA_Bel))
TAXA_all <- tax_table(TAXA_all)
Bel_all <- phyloseq(OTU_all, TAXA_all)
Bel_all <- tax_glom(Bel_all, taxrank = rank_names(Bel_all)[15])
Bel_all
iNEXT_table <- otu_table(Bel_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Bel <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#373461","#373461","#4c4987","#21203b","#4c4987","#21203b",
             "#373461","grey34","#21203b","#625ead","#4c4987","#4c4987",
             "#625ead","#21203b","#625ead","#373461","#625ead","#7570d1")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Bel, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Bel, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Bel, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Brazil sample

```{r Brazil}
Bra <- readRDS("phyloseq_Brazil_MiFish.rds")
Bra2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Brazil_MiFish_2.rds")
OTU_Bra2 <- as(otu_table(Bra2), "matrix")
OTU_Bra <- as(otu_table(Bra), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Bra2), as.data.frame(OTU_Bra))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Bra2 <- as(tax_table(Bra2), "matrix")
TAXA_Bra <- as(tax_table(Bra), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Bra2), as.data.frame(TAXA_Bra))
TAXA_all <- tax_table(TAXA_all)
Bra_all <- phyloseq(OTU_all, TAXA_all)
Bra_all <- tax_glom(Bra_all, taxrank = rank_names(Bra_all)[15])
Bra_all
iNEXT_table <- otu_table(Bra_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Bra <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#787424","#aba433","#aba433","#aba433","#aba433","#454215",
             "#787424","gray34","#454215","#787424","#454215","#454215",
             "#787424","gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Bra, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Bra, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Bra, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for CocosIsland sample

```{r CocosIsland}
Coco <- readRDS("phyloseq_CocosIsland_MiFish.rds")
Coco2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_CocosIsland_MiFish_2.rds")
OTU_Coco2 = as(otu_table(Coco2), "matrix")
OTU_Coco = as(otu_table(Coco), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Coco2), as.data.frame(OTU_Coco))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Coco2 <- as(tax_table(Coco2), "matrix")
TAXA_Coco = as(tax_table(Coco), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Coco2), as.data.frame(TAXA_Coco))
TAXA_all <- tax_table(TAXA_all)
Sample_Coco2 <- as(sample_data(Coco2), "matrix")
Sample_Coco <- as(sample_data(Coco), "matrix")
temp1 <- list(as.data.frame(Sample_Coco2), as.data.frame(Sample_Coco))
Sample_all <- RBIND(temp1, keep.rownames = TRUE)
Coco_all <- phyloseq(OTU_all, TAXA_all)
Coco_all <- tax_glom(Coco_all, taxrank = rank_names(Coco_all)[15])
Coco_all
iNEXT_table <- otu_table(Coco_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Coco <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#372038","#b669b8","#9c5a9e","#b669b8","#e786eb","#834c85",
             "#372038","#834c85","#834c85","#e786eb","#372038","#ce77d1",
             "#ce77d1","#ce77d1","#ce77d1","#372038","#9c5a9e","#9c5a9e",
             "#b669b8","#b669b8","#834c85","#e786eb","#834c85","#b669b8",
             "#834c85","#e786eb","gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Coco, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Coco, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Coco, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)


ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Coiba sample

```{r Coiba}
Coi <- readRDS("phyloseq_Coiba_MiFish.rds")
Coi2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Coiba_MiFish_2.rds")
OTU_Coi2 <- as(otu_table(Coi2), "matrix")
OTU_Coi <- as(otu_table(Coi), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Coi2), as.data.frame(OTU_Coi))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Coi2 <- as(tax_table(Coi2), "matrix")
TAXA_Coi <- as(tax_table(Coi), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Coi2), as.data.frame(TAXA_Coi))
TAXA_all <- tax_table(TAXA_all)
Coi_all <- phyloseq(OTU_all, TAXA_all)
Coi_all <- tax_glom(Coi_all, taxrank = rank_names(Coi_all)[15])
Coi_all
iNEXT_table <- otu_table(Coi_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Coi <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#4dd4d6","#246263","#5bf9fc","#3fadaf","#4dd4d6","#3fadaf",
                      "#4dd4d6","#4dd4d6","#5bf9fc","#32888a","#32888a",
                      "#5bf9fc","#246263","#3fadaf","#3fadaf","#246263",
                      "#32888a","#5bf9fc","#163d3d","#32888a","#246263",
                      "gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Coi, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Coi, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Coi, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Everglades sample

```{r Everglades}
Eve <- readRDS("phyloseq_Everglades_MiFish.rds")
Eve2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Everglades_MiFish_2.rds")
OTU_Eve2 <- as(otu_table(Eve2), "matrix")
OTU_Eve <- as(otu_table(Eve), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Eve2), as.data.frame(OTU_Eve))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Eve2 <- as(tax_table(Eve2), "matrix")
TAXA_Eve <- as(tax_table(Eve), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Eve2), as.data.frame(TAXA_Eve))
TAXA_all <- tax_table(TAXA_all)
Eve_all <- phyloseq(OTU_all, TAXA_all)
Eve_all <- tax_glom(Eve_all, taxrank = rank_names(Eve_all)[15])
Eve_all
iNEXT_table <- otu_table(Eve_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Eve <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#c86145","#7a3b2a","#7a3b2a","#7a3b2a","#c86145","#ed7351",
                      "#7a3b2a","#a14e37","#a14e37","#a14e37","gray34",
                      "#ed7351","#54291d","#a14e37","#c86145","#c86145",
                      "#ed7351","#7a3b2a","#ed7351","#54291d","#54291d",
                      "#54291d","gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Eve, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Eve, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Eve, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for LordHowe sample

```{r LordHowe}
Lor <- readRDS("phyloseq_LordHowe_MiFish.rds")
Lor2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_LordHowe_MiFish_2.rds")
OTU_Lor2 <- as(otu_table(Lor2), "matrix")
OTU_Lor <- as(otu_table(Lor), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Lor2), as.data.frame(OTU_Lor))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Lor2 <- as(tax_table(Lor2), "matrix")
TAXA_Lor <- as(tax_table(Lor), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Lor2), as.data.frame(TAXA_Lor))
TAXA_all <- tax_table(TAXA_all)
Lor_all <- phyloseq(OTU_all, TAXA_all)
Lor_all <- tax_glom(Lor_all, taxrank = rank_names(Lor_all)[15])
Lor_all
iNEXT_table <- otu_table(Lor_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Lor <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#542636","#7a374f","#7a374f","#c75980","#ed6b98","#ed6b98",
                      "#542636","#a14867","#a14867","#a14867","#a14867",
                      "#542636","#c75980","#c75980","#c75980","#7a374f",
                      "#7a374f","#ed6b98","gray34","#542636","#ed6b98","gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Lor, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Lor, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Lor, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Mauritania sample

```{r Mauritania}
Mau <- readRDS("phyloseq_Mauritania_MiFish.rds")
Mau2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Mauritania_MiFish_2.rds")
OTU_Mau2 <- as(otu_table(Mau2), "matrix")
OTU_Mau <- as(otu_table(Mau), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Mau2), as.data.frame(OTU_Mau))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Mau2 <- as(tax_table(Mau2), "matrix")
TAXA_Mau <- as(tax_table(Mau), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Mau2), as.data.frame(TAXA_Mau))
TAXA_all <- tax_table(TAXA_all)
Mau_all <- phyloseq(OTU_all, TAXA_all)
Mau_all <- tax_glom(Mau_all, taxrank = rank_names(Mau_all)[15])
Mau_all
iNEXT_table <- otu_table(Mau_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Mau <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#cf832d","#cf832d","#cf832d","#cf832d","#cf832d","#cf832d",
                      "#cf832d","#cf832d","#cf832d","#cf832d","#cf832d",
                      "gray34","#cf832d","#cf832d","#cf832d","#cf832d",
                      "#cf832d","#cf832d","#cf832d","#cf832d","#cf832d",
                      "#cf832d")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Mau, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Mau, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Mau, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Mexico sample

```{r Mexico}
Mex <- readRDS("phyloseq_Mexico_MiFish.rds")
Mex2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Mexico_MiFish_2.rds")
OTU_Mex2 <- as(otu_table(Mex2), "matrix")
OTU_Mex <- as(otu_table(Mex), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Mex2), as.data.frame(OTU_Mex))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Mex2 <- as(tax_table(Mex2), "matrix")
TAXA_Mex <- as(tax_table(Mex), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Mex2), as.data.frame(TAXA_Mex))
TAXA_all <- tax_table(TAXA_all)
Mex_all <- phyloseq(OTU_all, TAXA_all)
Mex_all <- tax_glom(Mex_all, taxrank = rank_names(Mex_all)[15])
Mex_all
iNEXT_table <- otu_table(Mex_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Mex <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#83b3fc","gray34","#344763","#698fca","#344763","#83b3fc",
                      "#83b3fc","#4e6b96","#83b3fc","#344763","#4e6b96",
                      "gray34","#698fca","#698fca","#344763","#83b3fc",
                      "#83b3fc","#4e6b96","#83b3fc","#698fca","#4e6b96",
                      "#83b3fc")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Mex, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Mex, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Mex, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for NewCaledonia sample

```{r NewCaledonia}
New <- readRDS("phyloseq_NewCaledonia_MiFish.rds")
New2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_NewCaledonia_MiFish_2.rds")
OTU_New2 <- as(otu_table(New2), "matrix")
OTU_New <- as(otu_table(New), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_New2), as.data.frame(OTU_New))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_New2 <- as(tax_table(New2), "matrix")
TAXA_New <- as(tax_table(New), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_New2), as.data.frame(TAXA_New))
TAXA_all <- tax_table(TAXA_all)
New_all <- phyloseq(OTU_all, TAXA_all)
New_all <- tax_glom(New_all, taxrank = rank_names(New_all)[15])
New_all
iNEXT_table <- otu_table(New_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_New <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#94ae35","#b4d43f","#d4fa4b","#94ae35","#738729","#52611d",
             "#738729","#b4d43f","#94ae35","#d4fa4b","gray34","#d4fa4b",
             "#52611d","#b4d43f","#52611d","#94ae35","#738729","#738729",
             "#52611d","#d4fa4b")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_New, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_New, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_New, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Ningaloo sample

```{r Ningaloo}
Nin <- readRDS("phyloseq_Ningaloo_MiFish.rds")
Nin2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Ningaloo_MiFish_2.rds")
OTU_Nin2 <- as(otu_table(Nin2), "matrix")
OTU_Nin <- as(otu_table(Nin), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Nin2), as.data.frame(OTU_Nin))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Nin2 <- as(tax_table(Nin2), "matrix")
TAXA_Nin <- as(tax_table(Nin), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Nin2), as.data.frame(TAXA_Nin))
TAXA_all <- tax_table(TAXA_all)
Nin_all <- phyloseq(OTU_all, TAXA_all)
Nin_all <- tax_glom(Nin_all, taxrank = rank_names(Nin_all)[15])
Nin_all
iNEXT_table <- otu_table(Nin_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Nin <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#bf81e3","#9f6cbd","#bf81e3","#7f5696","#3f2a4a","#9f6cbd",
             "#5f4070","#5f4070","#5f4070","#7f5696","#bf81e3","gray34",
             "#9f6cbd","#7f5696","#7f5696","#3f2a4a","gray34","#9f6cbd",
             "#3f2a4a","#bf81e3","#3f2a4a","#3f2a4a")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Nin, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Nin, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Nin, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Philippines sample

```{r Philippines}
Phi <- readRDS("phyloseq_Philippines_MiFish.rds")
Phi2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Philippines_MiFish_2.rds")
OTU_Phi2 <- as(otu_table(Phi2), "matrix")
OTU_Phi <- as(otu_table(Phi), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Phi2), as.data.frame(OTU_Phi))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Phi2 <- as(tax_table(Phi2), "matrix")
TAXA_Phi <- as(tax_table(Phi), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Phi2), as.data.frame(TAXA_Phi))
TAXA_all <- tax_table(TAXA_all)
Phi_all <- phyloseq(OTU_all, TAXA_all)
Phi_all <- tax_glom(Phi_all, taxrank = rank_names(Phi_all)[15])
Phi_all
iNEXT_table <- otu_table(Phi_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Phi <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#614416","#875f1f","gray34","#614416","#ad7a28","#3b290d",
             "#fab039","#614416","#ad7a28","#ad7a28","#875f1f","#875f1f",
             "#d39531","#d39531","#d39531","#875f1f","#ad7a28","#fab039",
             "#3b290d","#d39531","#614416","gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Phi, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Phi, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Phi, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Scandola sample

```{r Scandola}
Sca <- readRDS("phyloseq_Scandola_MiFish.rds")
Sca2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Scandola_MiFish_2.rds")
OTU_Sca2 <- as(otu_table(Sca2), "matrix")
OTU_Sca <- as(otu_table(Sca), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Sca2), as.data.frame(OTU_Sca))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Sca2 <- as(tax_table(Sca2), "matrix")
TAXA_Sca <- as(tax_table(Sca), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Sca2), as.data.frame(TAXA_Sca))
TAXA_all <- tax_table(TAXA_all)
Sca_all <- phyloseq(OTU_all, TAXA_all)
Sca_all <- tax_glom(Sca_all, taxrank = rank_names(Sca_all)[15])
Sca_all
iNEXT_table <- otu_table(Sca_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Sca <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#f26333","#f26333","#f26333","#f26333","#cc532b","#cc532b","#cc532b",
                  "#cc532b","#a64423","#a64423","#a64423","#a64423","#80341b",
                  "#80341b","#80341b","#80341b","#80341b","#592513","#33150b")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Sca, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Sca, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Sca, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Seychellen sample

```{r Seychellen}
Sey <- readRDS("phyloseq_Seychellen_MiFish.rds")
Sey2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Seychellen_MiFish_2.rds")
OTU_Sey2 <- as(otu_table(Sey2), "matrix")
OTU_Sey <- as(otu_table(Sey), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Sey2), as.data.frame(OTU_Sey))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Sey2 <- as(tax_table(Sey2), "matrix")
TAXA_Sey <- as(tax_table(Sey), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Sey2), as.data.frame(TAXA_Sey))
TAXA_all <- tax_table(TAXA_all)
Sey_all <- phyloseq(OTU_all, TAXA_all)
Sey_all <- tax_glom(Sey_all, taxrank = rank_names(Sey_all)[15])
Sey_all
iNEXT_table <- otu_table(Sey_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Sey <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#fc4e68","#fc4e68","#fc4e68","#d64259","#d64259","#d64259","#d64259",
                  "#b03749","#b03749","#b03749","#b03749","#8a2b39","#8a2b39",
                  "#8a2b39","#8a2b39","#631f29","#631f29","#631f29","#631f29")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Sey, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Sey, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Sey, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for SharkBay sample

```{r SharkBay}
Sha <- readRDS("phyloseq_SharkBay_MiFish.rds")
Sha2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_SharkBay_MiFish_2.rds")
OTU_Sha2 <- as(otu_table(Sha2), "matrix")
OTU_Sha <- as(otu_table(Sha), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Sha2), as.data.frame(OTU_Sha))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Sha2 <- as(tax_table(Sha2), "matrix")
TAXA_Sha <- as(tax_table(Sha), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Sha2), as.data.frame(TAXA_Sha))
TAXA_all <- tax_table(TAXA_all)
Sha_all <- phyloseq(OTU_all, TAXA_all)
Sha_all <- tax_glom(Sha_all, taxrank = rank_names(Sha_all)[15])
Sha_all
iNEXT_table <- otu_table(Sha_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Sha <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#e693ce","#e693ce","#e693ce","#e693ce","#bf7aac","#bf7aac","#bf7aac",
                  "#bf7aac","#bf7aac","#996289","#996289","#996289","#734967",
                  "#734967","#734967","#734967","#33202e","#33202e","#33202e",
                  "#33202e")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Sha, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Sha, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Sha, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for SouthAfrica sample

```{r SouthAfrica}
SoA <- readRDS("phyloseq_SouthAfrica_MiFish.rds")
SoA2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_SouthAfrica_MiFish_2.rds")
OTU_SoA2 <- as(otu_table(SoA2), "matrix")
OTU_SoA <- as(otu_table(SoA), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_SoA2), as.data.frame(OTU_SoA))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_SoA2 <- as(tax_table(SoA2), "matrix")
TAXA_SoA <- as(tax_table(SoA), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_SoA2), as.data.frame(TAXA_SoA))
TAXA_all <- tax_table(TAXA_all)
SoA_all <- phyloseq(OTU_all, TAXA_all)
SoA_all <- tax_glom(SoA_all, taxrank = rank_names(SoA_all)[15])
SoA_all
iNEXT_table <- otu_table(SoA_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_SoA <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#607fe6","#607fe6","#607fe6","#607fe6","#5b78d9","#5b78d9","#5b78d9",
                  "#5b78d9","#5b78d9","#4b63b3","#4b63b3","#4b63b3","#4b63b3",
                  "#3b4e8c","#3b4e8c","#3b4e8c","#3b4e8c","#2b3966","#2b3966",
                  "#2b3966","#2b3966")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_SoA, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_SoA, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_SoA, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for SouthernOcean sample

```{r SouthernOcean}
SoO <- readRDS("phyloseq_SouthernOcean_MiFish.rds")
SoO2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_SouthernOcean_MiFish_2.rds")
OTU_SoO2 <- as(otu_table(SoO2), "matrix")
OTU_SoO <- as(otu_table(SoO), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_SoO2), as.data.frame(OTU_SoO))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_SoO2 <- as(tax_table(SoO2), "matrix")
TAXA_SoO <- as(tax_table(SoO), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_SoO2), as.data.frame(TAXA_SoO))
TAXA_all <- tax_table(TAXA_all)
SoO_all <- phyloseq(OTU_all, TAXA_all)
SoO_all <- tax_glom(SoO_all, taxrank = rank_names(SoO_all)[15])
SoO_all
iNEXT_table <- otu_table(SoO_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_SoO <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#52faf4","#52faf4","#52faf4","#52faf4","#52faf4","#42c7c2","#42c7c2",
                  "#42c7c2","#42c7c2","#319491","#319491","#319491","#319491",
                  "#20615f","#20615f","#20615f","#20615f","#20615f","#0f2e2d",
                  "#0f2e2d","#0f2e2d","#0f2e2d")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_SoO, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_SoO, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_SoO, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Wadden sample

```{r Wadden}
Wad <- readRDS("phyloseq_Wadden_MiFish.rds")
Wad2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Wadden_MiFish_2.rds")
Wad3 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_WaddenB_MiFish_2.rds")
OTU_Wad2 <- as(otu_table(Wad2), "matrix")
OTU_Wad <- as(otu_table(Wad), "matrix")
OTU_Wad3 <- as(otu_table(Wad3), "matrix")
OTU_all <- plyr::rbind.fill(as.data.frame(OTU_Wad2), as.data.frame(OTU_Wad), as.data.frame(OTU_Wad3))
OTU_all[is.na(OTU_all)] <- 0
OTU_all <- otu_table(OTU_all, taxa_are_rows = TRUE)
TAXA_Wad2 <- as(tax_table(Wad2), "matrix")
TAXA_Wad <- as(tax_table(Wad), "matrix")
TAXA_Wad3 <- as(tax_table(Wad3), "matrix")
TAXA_all <- plyr::rbind.fill(as.data.frame(TAXA_Wad2), as.data.frame(TAXA_Wad), as.data.frame(TAXA_Wad3))
TAXA_all <- tax_table(TAXA_all)
Wad_all <- phyloseq(OTU_all, TAXA_all)
Wad_all <- tax_glom(Wad_all, taxrank = rank_names(Wad_all)[15])
Wad_all
iNEXT_table <- otu_table(Wad_all) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Wad <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#73ff6e","#73ff6e","#73ff6e","#73ff6e","#73ff6e","#73ff6e","#73ff6e",
                  "#73ff6e","#73ff6e","#61d95d","#61d95d","#61d95d","#61d95d",
                  "#61d95d","#61d95d","#61d95d","#61d95d","#61d95d","#50b34d",
                  "#50b34d","#50b34d","#50b34d","#50b34d","#50b34d","#50b34d",
                  "#50b34d","#50b34d","#3f8c3c","#3f8c3c","#3f8c3c","#3f8c3c",
                  "#2e662c","#2e662c","#2e662c","#2e662c","#2e662c","#2e662c",
                  "#2e662c","#2e662c","#2e662c","#2e662c")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Wad, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Wad, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Wad, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```


# Plot rarefaction curves of Mifish amplicon for Yemen sample

```{r Yemen}
Yem2 <- readRDS("../../2nd_batch/rarefaction_curves/phyloseq_Yemen_MiFish_2.rds")
Yem2 <- tax_glom(Yem2, taxrank = rank_names(Yem2)[15])
Yem2
iNEXT_table <- otu_table(Yem2) %>% t() %>% data.frame()
iNEXT_input <- as.list(as.data.frame(t(iNEXT_table)))
iNEXT_data_Yem <- iNEXT(iNEXT_input, q = c(0), datatype = "abundance")

palette <- c("#030102","#ff66cc","#331429","#cc52a3","#ff66cc","#662952",
             "#993d7a","gray34")

# Sample-size-based rarefaction/extrapolation curve
p1 <- ggiNEXT(iNEXT_data_Yem, type=1, color.var = "Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Sample completeness curve
p2 <- ggiNEXT(iNEXT_data_Yem, type=2, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

# Coverage-based rarefaction/extrapolation curve
p3 <- ggiNEXT(iNEXT_data_Yem, type=3, color.var="Assemblage") +
  scale_colour_manual(values=palette) +
  scale_fill_manual(values=palette)

ggarrange(p1, p2, p3 + rremove("x.text"), 
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2, common.legend = T, legend = "right")

```
